Self Regulation Ontology Retest Analyses

### 2018-06-06 code/SRO_Retest_Analyses.Rmd
started meaningful var analyses

Dealing with this:
using the measures you found in the literature
using ian's function

```{r}

>>>>

We have a list of measures we extracted from the literature as the canonical ones used for analyses.

```{r}
meaningful_vars = read.table('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/meaningful_vars.txt')
meaningful_vars = as.character(meaningful_vars$V1)

tmp = as.character(unique(lit_review$dv)[which(unique(lit_review$dv) %in% meaningful_vars == FALSE)])
tmp = tmp[-grep('survey', tmp)]

meaningful_vars = c(meaningful_vars, tmp)
meaningful_vars = sort(meaningful_vars)
```
